\begin{problem}{Way via mountains}{stdin}{stdout}{1 second}{64 megabytes}

The highlands' surface can be presented as a polygonal chain with vertices at the points $(x_1,y_1)$, $(x_2,y_2)$,~\dots, $(x_N,y_N)$, moreover $x_i<x_{i+1}$.
Ordinary mountain's magus staying at $(x_1,y_1)$ wants to move to the point $(x_N,y_N)$. He~can move only afoot. He can walk on the surface of the Earth (along the polygonal chain). However, he also can create a bridge in the air and walk through it. The bridge can connect two vertices of the polygonal chain: the bridge should start and finish in some vertices of the polygonal chain and the bridge can't go underground (so it shouldn't form a tunnel in the mountain), but some points or segments of the bridge can touch the surface of the earth.
The bridge can't be longer than~$R$. Magus can't build more than $K$ bridges. After passing a bridge, it disappears in the air. What the minimum distance magus should pass to move to the point $(x_N,y_N)$?

\InputFile
The program should read firstly positive integer $N$ ($2\leq N\leq 555$);
then a positive integer $K$ ($1\leq K\leq 256$) ---
the maximum number of bridges;
then an integer $R$ ($0\leq R\leq 10000$) --- maximum
possible length of the bridge. Next, the coordinates $(x_1,y_1)$, $(x_2,y_2)$,~\dots, $(x_N,y_N)$.
All coordinates are integers and aren't exceeding $10000$ by absolute value.
$x_i<x_{i+1}$ is true for all~$i$ from $1$ to~$N$--1.

\OutputFile
The program should print a single number --- the minimum length of path magus have to pass (both on the ground and through the bridges).
Print answer to within 6 digits after the decimal point.

\Examples

\begin{example}
\exmp{5 2 5
0 0
2 2
3 -1
4 1
5 0
}{6.4787086646190746
}%
\end{example}

\end{problem}
